---
title: "Lab 14"
author: "Lauren, Ryan, Katie, Chris"
date: "4/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(purrr)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`) #renaming `bwt/oz` because the "/" sign requires special care

babies1 <- na.omit(babies)
```

# Overall Question
1. Does Smoking Lead to Babies Born Prematurely?
2. Does Smoking lead to Babies with Low Birth Weight?

## Why it is interesting?
 Generally speaking, smoking is harmful to our body. But in society, a lot of people still smoke and the tendency for women to smoke during preagnancy is increasing, which may have some negative effect on next generation. Babies are significant in a family, and also important for our future, thus in order to figure out what kind of effect of smoking will lead to on both mothers and babies, we analyzed whether smoking leads to babies born prematurely and whether smoking lead to babies with low birth weight. These results will give us solid insight on smoking's effects on babies and mothers. 
## What new tools that we applied?

## The new answers comparing to previous lab

# Conclusion

# Individual Findings

## Lauren 
### Subquestion


## Katie
### Subquestion
Does short gestation days causes light babies weight based on smoking and nonsmoking?
#### why it is important?
Because the short gestation days may lead light babies weight directly, and I think it is an important part for answering our overall questions.And generally speaking, we all think it will cause light weight, but is there a real relationship between them ? I want to explore it more deeply.

#### New tool I used
In order to find the relationship between gestation days and the babies weight, I build a new model which is linear relationship of log gestation days with log weight. Because taking log will make our data more clear and easier to see the tendency. And I add predictions and residuals to see the difference between model and the real data.
```{r}
babies1 <- babies1 %>% filter(gestation <= 270) %>% 
  mutate(lweight = log(bwtoz),lges= log(gestation)) %>% select(gestation,bwtoz,lweight,lges,number,smoke) 

ggplot(babies1,aes(lges,lweight))+
  geom_hex(bins = 50)+
  geom_smooth(method = "loess")+
  facet_wrap(~smoke)+
  ggtitle("Tendency of gestation days with weight")

model_babies1 <-lm(lweight~lges,data = babies1)
```
I use data_grid to create a model data for gestation days and babies weight, and put the estimated one with the real data together.

```{r}
grid <- babies1 %>% 
  data_grid(gestation = seq_range(gestation,270))%>%
  mutate(lges = log2(gestation))%>%
  add_predictions(model_babies1,"lweight")%>%
  mutate(bwtoz = 2^lweight)


ggplot(babies1, aes(gestation,bwtoz )) + 
  geom_hex(bins = 50) + 
  geom_line(data = grid, colour = "red", size = 1)+
  facet_wrap(~smoke)+
  ggtitle("Linear model with real data")

```
We can see from the plot above, there are lots of babies weight above the linear model for nonsmoking one, and more points are below for smoking group. And the majority of points are lying much more above in nonsmoking than smoking group.

```{r}
babies1 <- babies1 %>%
  add_residuals(model_babies1,"lreids")
ggplot(babies1,aes(lweight,lreids))+
  geom_hex(bins = 50)+
  geom_smooth(method = "loess")+
  ggtitle("residuals with lweight data")
ggplot(babies1, aes(as.character(gestation), lreids)) + geom_boxplot()+
  coord_flip()+
  facet_wrap(~smoke)+
  ggtitle("Smoke vs. Nonsmoke the residuals of gestation days")
```
Because there are many points above the linear model, so I looked at the residuals for the weight. In the first graph, there is a tendency of residuals along with weight. After that, I plot the blox plot of residuals and gestation days. The residuals for nonsmoking are larger than the smoking one, and that is what we are expected.
Thus the final answer is that the short gestation days affect babies weight, especially for smoking mothers. And it is an important part of our overall question, because smoking may affect the gestation days, which will cause permature, and that have the relation with babies weight.

## Ryan
### Subquestion
What is the difference between the income distributions of smokers vs. nonsmokers?
#### why it is important?
This question is imporatnt because it gives some insight on whether a person's income has any relationship with the likleyhood that they will be a smoker. With this information, one could target specific income groups with information about the dangers of smoking, hopefully causing greater change.

#### New tool I used
I used a while loop to manipulate a certain variable in my data frame. I also used fitting to explore trends in the data more deeply. Here, I observed the qualities of the fit, and used it to draw a conclusion about my dataset. I then observed the residuals of the fit, and attempted to justify whether or not the fit was any good. This was a very old lab, so I also implemented some dyplyr tools that were obviously useful here, which I am glad I know now, but wish I knew then. I also used the cor() function to get a preliminary idea of the relationship between income and smoking. 



```{r}
ggplot(subset(babies,smoke!= "NA"),mapping = aes(x=inc))+
  geom_bar(aes(y=..prop..,fill=..x..))+scale_fill_gradient(low="gray",high="yellow")+
  facet_wrap(~smoke)+labs(x = "Income",y="Proportion",title = "Income Distributions of Smokers vs. Non-Smokers")
  
```

Here is shown the distribution of the proportion of people in each income group for smokers, and for non-smokers. It seems as if nonsmokers have a slightly greater density in the 4 lowest income groups than smokers. Also it seems as if smokers have a greater density in the middle income grops (3-5). To further explore this relationship, I will maniuplate the data in such a way that I can show the difference in 



```{r}
count_inc<-babies%>%group_by(inc)%>%count()
count_inc<-count_inc$n
babies_psmoke<-babies%>%group_by(inc)%>%arrange(inc)%>%filter(!is.na(smoke))%>%filter(!is.na(inc))%>%summarise(psmoke = sum(smoke))

i <-1
while (i<=10) {
  babies_psmoke[i,2] = babies_psmoke[i,2]/count_inc[i]
  i<-i+1
}


ggplot(data = babies_psmoke, aes(x = inc,y = psmoke))+
 geom_point()+
  geom_smooth()
  
```


```{r}
cor(babies_psmoke$inc,babies_psmoke$psmoke)
```

It seems like the proportion of those people who smoke is very weakly correlated with income. It also seems like there is a peak of smoking frequency for the "middle class" income groups.


With some preliminary information about the relationship between income group and proportion of smokers, I will try to fit a low order polynomial to the data, and see if any more information about the trends can be gathered
```{r}
model_psmoke <-lm(data = babies_psmoke,psmoke~poly(inc,2))

babies_psmoke<-babies_psmoke%>%add_predictions(model_psmoke)%>%add_residuals(model_psmoke)

ggplot(babies_psmoke,aes(x = inc))+
  geom_point(aes(y = psmoke))+
  geom_line(aes(y = pred),color = 'red')

```

The low degree polynomial fit (a degree 2 polynomial) seems to confirm the suspicion that middle income groups temd to be more likley to be smokers than either high or low income groups. It seems, however that the data fits fairly poorly, so it would be useful to look at the residuals, to gauge just how skeptical one should be about this conclusion.
```{r}

ggplot(babies_psmoke,aes(x = inc))+
  geom_col(aes(y = abs(resid/psmoke)))

```
Here is plotted the "percent residual" for each of the data points, when using the degree two fit. This shows, that in general the model is closer than a 10% error, but has an error of above 15% in one case. This type of error would suggest to me a very poor fit of the data. The conclusion to be drawn from this is that there may be a higher liklihood for middle class income people to smoke, however more research is needed to solidify that conclusion.

## Chris

### Subquestion
how is the relationship between gestation day the people who smoke? does smoke lead premature?

#### why it is important?
cause at right now, most of people thought that when u smoke durning ur pregancy period, u got more prob that premature, so i want to find this is true or not and the prob that i can calculate. 

#### New tool I used
at first i used the select function to mutate what variable that i need. "gestation " and "smoke" to be honest, it doesnt matter. than i used filter function to calculate and count the variable that i got. maybe the things that i learned from our lab 10 or lab11. than i just do the divide part to get a exact number to find my value.

```{r}
babies1<-select(babies, gestation, smoke)
gg270<-babies1 %>% filter(gestation>=270)%>% count()
gl270<-babies1 %>% filter(gestation<270)%>% count()

gw<-babies1 %>% filter(smoke=="1")%>% count()
gwo<-babies1 %>% filter(smoke=="0")%>% count()

ggwo270<-babies1 %>% filter(gestation>=270 & smoke=="0")%>% count()
glwo270<-babies1 %>% filter(gestation<270 & smoke=="0")%>% count()

ggw270<-babies1 %>% filter(gestation>=270 & smoke=="1")%>% count()
glw270<-babies1 %>% filter(gestation<270 & smoke=="1")%>% count()
```
this steps just kind of filter steps and than count the value that i need for the fulture.
gg270 means gestation day>=270 days, gl270 means less, gw means the number of people who smoke, gwo means people who doesnot smoke, ggw270 means gestation day>=270 and smoke, glw270 means gestation<270 and smoke, ggwo270 means people who gestation day>=270 and doesnt smoke. on the contrary, glwo270 means gestation day<270 and dont smoke.

```{r}
#after 270 genestion
ggw270/gg270 #who smoke gestation>=270 /gestation>270
ggwo270/gg270  #who doesnt smoke gestatio>=270 /gestation>270


#before 270 
glw270/gl270  #who smoke gestation<270 /gestation<270
glwo270/gl270  #who doesnt smoke gestation<270 /gestation<270

```

```{r}
ggw270/gw #who smoke gestation>=270/people who smoke #0.7789
glwo270/gwo #who doesnt smoke gestation>=270/people who doesnt smoke #0.1673
```
the next two steps i just do some calculate steps, in the end, i found that people who smoke have more prob that the gestation day greater or equal to the 270 days. but people who doesnt smoke have less prob that the gestation day greater or equal to the 270 days. it is wired and seems breaks our mind but that the things that i found.

## Contributions
### Lauren 


### Katie
I outlined the lab14, and put overall questions and the importance part.Then I modified my original individual question and answered it by creating model of gestation days with babies weight.In the model, I created a data_grid to simulate the real data and put them together to observe the residuals and the predictions.

### Chris
I did my individual part on time, and tried to analaysis the subquestion i made. whether the smoke or not will influence the pregency thing. I used some filter function and count the number that i got to. than i divide the two variable that i got tried to find the prob that i need. final, i found that the results looks the same as I did before in lab4, the smoke doesnt make any bay influence in geastation day.

### Ryan



