<<<<<<< HEAD

---
title: "Lab11"
author: "Lauren Gregg, Katie Jiang, Ryan Marizza, Chris He"
date: "4/06/2018"
output: html_document
---


```{r setup, include=FALSE}
library(babynames)
library(stringr)
library(tidyverse)
rm(list=ls()) # clears your environment variables

```
#Analyzing Baby Names
# Team Work

 
# Individual Work
 

## Lauren
## First three letters of names
## Ariel and Rachel regexs
## The Little Mermaid Effect
## Your names


## Kaite
## First three letters of names

```{r}
sum(str_count(babynames$name,"Kat"))
sum(str_count(babynames$name,"kat"))
```
ratio of "Kat" = 0.96
## Ariel and Rachel regexs

```{r}
Rach1973 <- filter(babynames,str_detect(babynames$name,"^Rach[:lower]*l"),year==1973,sex =="F")%>% count()
Rach1988 <- filter(babynames,str_detect(babynames$name,"^Rach[:lower]*l"),year==1988,sex =="F")%>% count()
Rach1990 <- filter(babynames,str_detect(babynames$name,"^Rach[:lower]*l"),year==1990,sex =="F")%>% count()
Rach1973
Rach1988
Rach1990

Arie1973 <- filter(babynames,str_detect(babynames$name,"Ariel"),year==1973,sex =="F")%>%count()
Ariel1988 <-  filter(babynames,str_detect(babynames$name,"Ariel"),year==1988,sex =="F")%>% count()
Ariel1990 <-  filter(babynames,str_detect(babynames$name,"Ariel"),year==1990,sex =="F")%>% count()
Arie1973
Ariel1988
Ariel1990

g1973 <- filter(babynames,year == 1973, sex == "F") %>% count()
chance1973 <- (Rach1973+Arie1973)/g1973
chance1973
g1988 <- filter(babynames,year == 1988,sex == "F") %>% count()
chance1988 <- (Rach1988+Ariel1988)/g1988
chance1988

g1990 <- filter(babynames, year == 1990, sex == "F") %>% count()
chance1990 <- (Rach1990+Ariel1990)/g1973
chance1990
```
The number of versions for Rachel in 1973 is 5, in 1988 is 7, and in 1990 is 5.
The number of versions for Ariel in 1973 is 3, in 1988 is 6, and in 1990 is 6.
The chances of girl bron in 1973 named Rachel or Ariel is 0.000816, in 1988 is 0.000937, and in 1990 is 0.00122
## The Little Mermaid Effect

```{r}
girl <- babynames%>%filter(sex == 'F')
names<-girl%>%filter(str_detect(name,"^A"))%>%filter(year == 1988 | year == 1990)

n1988<-names%>%filter(year == 1988)
n1990<-names%>%filter(year == 1990)

Adiff<-left_join(n1988,n1990,by = 'name')%>%mutate(diff = prop.x-prop.y)%>% select(name,prop.x,prop.y,diff)

Ariel.diff <- filter(babynames,str_detect(babynames$name,"Ar[iy]+.l+[^a]?$"),year==1990,sex=="F") %>% count(wt=prop) - filter(babynames,str_detect(babynames$name,"Ar[iy]+.l+[^a]?$"),year==1988,sex=="F") %>% count(wt=prop)
Ariel.diff
# the percentile of Ariel changes
filter(Adiff,diff<Ariel.diff) %>% arrange(desc(diff))
filter(Adiff,diff<Ariel.diff) %>% count()/names %>% count()


ggplot(Adiff) +
  geom_histogram(aes(x=diff),bins=50) + xlim(-0.003,0.003)+
  geom_vline(aes(xintercept=Ariel.diff),color="red",lwd=1) 

```
The percentile of changing to Ariel is 100%, because there is no other names with difference that is bigger than Ariel. The other girls' name has the distribution aroud 0, which means they have slightly changes. However, the difference for Ariel is far away on the right side of the plot, which means it has a great change. Thus, comparing to other girl's names, the Ariel have a bigger change over time.
## Your names

```{r}
my <- babynames %>% filter(sex == "F")
ka <- my %>% filter(str_detect(name,"^Katie")) %>% filter(year == 1998 | year == 2015)
n1998 <- ka %>% filter(year == 1998)
n2015 <- ka %>% filter(year == 2015)
changeka <- left_join(n1998,n2015, by = "name") %>% mutate(diff = prop.x- prop.y) %>% count(wt = diff)
changeka

ka1981 <- my %>%filter(str_detect(name,"^Katie")) %>% filter(year == 1981 | year == 1998)
n1981 <- ka1981 %>% filter(year == 1981)
changeka2 <- left_join(n1981,n1998, by = "name") %>% mutate(diff = prop.x - prop.y) %>% count(wt = diff)
changeka2

all98<- filter(babynames,year == 1998)
all15<- filter(babynames,year == 2015)
```
My name Katie have the difference 0.00138 from 1998 to 2015, and have 0.00177 from 1981 to 1998.

```{r}
#actucal change in propotion
Katie.diff <- filter(babynames,str_detect(babynames$name,"^Katie"),year==1998,sex=="F") %>% count(wt=prop) - filter(babynames,str_detect(babynames$name,"^Katie"),year==2015,sex=="F") %>% count(wt=prop)
Katie.diff
#relative change in precentile
Kgirl <- filter(babynames,str_detect(babynames$name , "^K"),year == 1998|year == 2015)
n1998 <- Kgirl %>% filter(year == 1998)
n2015 <- Kgirl %>% filter(year == 2015)

Kdiff<-left_join(n1998,n2015,by = 'name')%>%mutate(diff = prop.x-prop.y)%>% select(name,prop.x,prop.y,diff)

filter(Kdiff,diff<Katie.diff) %>% arrange(desc(diff))
filter(Kdiff,diff<Katie.diff) %>% count() 

#plot shows the difference
inner_join(all98,all15,by = "name") %>% mutate(df = prop.x-prop.y)%>%
  select(name,prop.x,prop.y,df)%>%
  ggplot()+geom_histogram(mapping = aes(x = df),bins = 40)+xlim(-0.003,0.003)+
  geom_vline(aes(xintercept = changeka),color = "red",lwd =1)+
  labs(x = "Difference", y ="Count", title = "The changes of Katie between 1998 and 2015")

```
The actucal change for Katie is 0.00138, and the relative change is 100% from 1998 to 2015, which is the percentile. Because there is no other names have the bigger changes than mine, which we could also see from the plot.

```{r}
#actucal change in propotion
Katie.diff1 <- filter(babynames,str_detect(babynames$name,"^Katie"),year==1981,sex=="F") %>% count(wt=prop) - filter(babynames,str_detect(babynames$name,"^Katie"),year==1998,sex=="F") %>% count(wt=prop)
Katie.diff1
#relative change in precentile
Kgirl1 <- filter(babynames,str_detect(babynames$name , "^K"),year == 1998|year == 1981)
n1998 <- Kgirl %>% filter(year == 1998)
n1981 <- Kgirl %>% filter(year == 2015)

Kdiff1<-left_join(n1998,n1981,by = 'name')%>%mutate(diff = prop.x-prop.y)%>% select(name,prop.x,prop.y,diff)
Kdiff1
filter(Kdiff1,diff< Katie.diff1) 
filter(Kdiff1,diff<Katie.diff1) %>% count() /Kgirl1 %>% count()

#plot shows the change
all81 <- filter(babynames,year == 1981)
inner_join(all81,all98, by = "name")%>%
  mutate(df = prop.x-prop.y)%>%
  select(name,prop.x,prop.y,df)%>%
  ggplot()+geom_histogram(mapping = aes(x = df),bins = 30)+xlim(-0.01,0.01)+
  geom_vline(aes(xintercept = changeka2),color = "red",lwd=1)+
  labs(x = "Difference", y ="Count", title = "The changes of Katie between 1981 and 1998")
```
The actual change for Katie from 1981 to 1998 is 0.00177, and the relative change in percentile is 100%. And we can see from the plot that my name become more popular comparing to others



## Ryan
```{r}
data<-babynames
names<-data$name
```
## First three letters of names
```{r}
Ryan_ratio = sum(str_count(names,"Rya"))/(sum(str_count(names,"Rya"))+sum(str_count(names,"rya")))
Lauren_ratio = sum(str_count(names,"Lau"))/(sum(str_count(names,"Lau"))+sum(str_count(names,"lau")))
Katie_ratio = sum(str_count(names,"Kat"))/(sum(str_count(names,"Kat"))+sum(str_count(names,"kat")))
Chris_ratio = sum(str_count(names,"Chr"))/(sum(str_count(names,"Chr"))+sum(str_count(names,"chr")))


data_ryan <- data%>%group_by(year)%>%summarise(prop_rya = sum(str_count(name,"Rya"))/sum(str_count(name,"")))
data_lauren <- data%>%group_by(year)%>%summarise(prop_lau = sum(str_count(name,"Lau"))/sum(str_count(name,"")))
data_katie <- data%>%group_by(year)%>%summarise(prop_kat = sum(str_count(name,"Kat"))/sum(str_count(name,"")))
data_chris <- data%>%group_by(year)%>%summarise(prop_chr = sum(str_count(name,"Chr"))/sum(str_count(name,"")))


Ryan_ratio
Lauren_ratio
Katie_ratio
Chris_ratio
```
These show the total ratios of each team members first three letters of their name to the total times those three letters were seen in names.

The following plots display how the relative frequency of each persons' name's first three letters changes through time.


```{r}
ggplot(data = data_ryan,aes(x=year,y=prop_rya))+
  geom_line()
```

The relative frequency of the use of my name spikes in the 1980's, and continues to be high through 2015. This makes sense, since I was born in 1996.


```{r}
ggplot(data = data_lauren,aes(x=year,y=prop_lau))+
  geom_line()


```

```{r}
ggplot(data = data_katie,aes(x=year,y=prop_kat))+
  geom_line()


```

```{r}
ggplot(data = data_chris,aes(x=year,y=prop_chr))+
  geom_line()
```


## Ariel and Rachel regexs
```{r}
#Ariel/Rachel
girl<-data%>%filter(sex == 'F')
girls<-girl$name

g1973<-girl%>%filter(year == 1973)
count1973<-g1973%>%count()
sum(str_count(g1973$name,"^Rach[:lower:]*l$|^Raych[:lower:]*l$"))
sum(str_count(g1973$name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))

g1973_rach <- g1973%>%filter(str_detect(name,"^Rach[:lower:]*l$|^Raych[:lower:]*l$"))%>%summarise(p_rach = sum(prop))
g1973_ari <- g1973%>%filter(str_detect(name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))%>%summarise(p_ari = sum(prop))



g1988<-girl%>%filter(year == 1988)
count1988<-g1988%>%count()
sum(str_count(g1988$name,"^Rach[:lower:]*l$|^Raych[:lower:]*l$"))
sum(str_count(g1988$name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))

g1988_rach <- g1988%>%filter(str_detect(name,"^Rach[:lower:]*l$|^Raych[:lower:]*l$"))%>%summarise(p_rach = sum(prop))
g1988_ari <- g1988%>%filter(str_detect(name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))%>%summarise(p_ari = sum(prop))


g1990<-girl%>%filter(year == 1990)
count1990<-g1990%>%count()
sum(str_count(g1990$name,"^Rach[:lower:]*l$|^Raych[:lower:]*l$"))
sum(str_count(g1990$name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))

g1990_rach <- g1990%>%filter(str_detect(name,"^Rach[:lower:]*l$|^Raych[:lower:]*l$"))%>%summarise(p_rach = sum(prop))
g1990_ari <- g1990%>%filter(str_detect(name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))%>%summarise(p_ari = sum(prop))


```
It is interesting to note that the number of variations of the name "Ariel" increases from 1973 to 1988 and again to 1990.

## The Little Mermaid Effect
```{r}
#Change in proportion of female Ariel names
g_both <- left_join(g1988,g1990,'name')

gen_change<- g_both%>%filter(str_detect(name,"[AEIOU]"))%>%mutate(change = (prop.y-prop.x)/((n.x+n.y)/2))
ariels_change<- g_both%>%filter(str_detect(name,"Ar[iy]+.l+[^ayi]$|Arial|Ariale|Arialle"))%>%mutate(change = (prop.y-prop.x)/((n.x+n.y)/2))
ariel_mean<-ariels_change%>%summarise(change = mean(change))
ngen_change<-gen_change%>%count()
nsmall_change<-gen_change%>%filter(change<ariel_mean$change)%>%count()

ariel_change_percentile<-nsmall_change$n/ngen_change$n
#81st percentile!

#plot between changes in other female names and changes of ariel names
ggplot()+
  geom_point(data = gen_change, aes(x = name, y=change))+
  geom_point(data = ariels_change, aes(x=name, y= change,color='red'))



```
The analysis showed that Ariel names changes more than 81% of all names. That is, Ariel names were in the 81st percentile of change from 1988 to 1990.

This plot shows the change in the proportion of various names from 1988 to 1990. Names below the zero line decreased in relative popularity, while names above the zero line increased in relative popularity. The points on this plot (near the middle) which are red represent the change in popularity of different variations of the name "Ariel". The important thing to note from this plot is that the Ariel names increased in popularity more than most other names.

The change in proportion of names was normalized by the count to avoid biasing such that more popular names (which will obviously have a higher raw change than less popular names) are not at an unfair advantage.

## Your names



For this analysis, year/gender was delt with by writing a conditional filter which filtered for the team member's gender and birth year as it was filtering for his/her name. This was impossible to do for the whole data set, so the median year, 1997, was chosen as the representative.

The change in proportion of names was normalized here in a similar fashion as above. 
```{r}
rel_data_BY = data%>%filter(year == 1997)
rel_data_15 = data%>%filter(year == 2015)
rel_data_X = data%>%filter(year == 1979)


rel_data_change1 = left_join(rel_data_BY,rel_data_15,by = 'name')%>%filter(!is.na(year.y))%>%mutate(change = abs(prop.y-prop.x)/(n.x+n.y))
rel_data_change2 = left_join(rel_data_BY,rel_data_X,by = 'name')%>%filter(!is.na(year.y))%>%mutate(change = abs(prop.y-prop.x)/(n.x+n.y))




birth_year<-data%>%filter((str_detect(name,"R[yi][ae]n$") & year == 1997)& sex == 'M' |(str_detect(name,"Laur[ea]n+$") & year == 1996)& sex == 'F' | (str_detect(name,"[CK]atie$|[CK]aty$") & year == 1998)& sex == 'F'|(str_detect(name,"Chris$|Kris$|Cris$") & year == 1998)& sex == 'M'   )

year_2015<-data%>%filter((str_detect(name,"R[yi][ae]n$") & year == 2015)& sex == 'M' |(str_detect(name,"Laur[ea]n+$") & year == 2015)& sex == 'F' | (str_detect(name,"[CK]atie$|[CK]aty$") & year == 2015)& sex == 'F'|(str_detect(name,"Chris$|Kris$|Cris$") & year == 2015)& sex == 'M'   )

year_X<-data%>%filter((str_detect(name,"R[yi][ae]n$") & year == 1979)& sex == 'M' |(str_detect(name,"Laur[ea]n+$") & year == 1978)& sex == 'F' | (str_detect(name,"[CK]atie$|[CK]aty$") & year == 1980)& sex == 'F'|(str_detect(name,"Chris$|Kris$|Cris$") & year == 1980)& sex == 'M'   )



change1<-left_join(birth_year,year_2015,by="name")%>%filter(!is.na(year.y))

change1<-change1%>%mutate(change = abs(prop.y-prop.x)/(n.x+n.y))%>%mutate(is_significant = (change<1e-07))

change2<-left_join(birth_year,year_X,by='name')%>%filter(!is.na(year.y))
change2<-change2%>%mutate(change = abs(prop.y-prop.x)/(n.x+n.y))%>%mutate(is_significant = (change<1e-07))

ggplot(data = change1,aes(y=change,x=name,fill=is_significant))+
  geom_col()

```

```{r}
ggplot(data = change2,aes(y=change,x=name,fill=is_significant))+
  geom_col()
```

From these plots, it seems that variations of Chris, and some variations of Ryan have a significantly low change throughout the years. (They were around the fifth percentile of change).

```{r}
total_count1<-rel_data_change1%>%count()
ryan_count1<-rel_data_change1%>%filter(change<2.102606e-07)%>%count()
lauren_count1<-rel_data_change1%>%filter(change<3.397108e-07)%>%count()
katie_count1<-rel_data_change1%>%filter(change<2.900464e-07)%>%count()
chris_count1<-rel_data_change1%>%filter(change<1.573157e-08)%>%count()


total_count2<-rel_data_change2%>%count()
ryan_count2<-rel_data_change2%>%filter(change<6.125439e-08)%>%count()
lauren_count2<-rel_data_change2%>%filter(change<2.667051e-07)%>%count()
katie_count2<-rel_data_change2%>%filter(change<1.546803e-07)%>%count()
chris_count2<-rel_data_change2%>%filter(change<1.489500e-07)%>%count()




ryan_pct_change1 <- ryan_count1/total_count1
lauren_pct_change1 <- lauren_count1/total_count1
katie_pct_change1 <- katie_count1/total_count1
chris_pct_change1 <- chris_count1/total_count1


ryan_pct_change2 <- ryan_count2/total_count2
lauren_pct_change2 <- lauren_count2/total_count2
katie_pct_change2 <- katie_count2/total_count2
chris_pct_change2 <- chris_count2/total_count2


#Percentiles
ryan_pct_change1$n
lauren_pct_change1$n
katie_pct_change1$n
chris_pct_change1$n

ryan_pct_change2$n
lauren_pct_change2$n
katie_pct_change2$n
chris_pct_change2$n
```

The perecntile of change from birth year to 2015 and birth year to birth year - X were computed as well. It seems like the name "Chris" had by far the lowest percent change from birth year to 2015, where the name"Lauren" had the highest. The name "Ryan" had the lowest change from year X to birth year, and the name "Lauren" had the highes percent change from birth year to 2015.
 
## Chris
## First three letters of names
## Ariel and Rachel regexs
## The Little Mermaid Effect
## Your names


# Summary of Who did What

## Lauren


## Kaite
I outlined the lab11 and divided each section for each teammates. In my individual part, I first found the ratio of first three letters of my name by using str_count. And I found the number of versions of Ariel and Rachel in 1973,1988 and 1990. The number of difference is increasing, which indicates that there is a effect to names based on The Little Mermaid. Then to prove it, I plot the change for Ariel from 1988 to 1990. Lastly, for my names, I plot two histograms to show the changes from the year that I was born to 2015 and from 17 years before I was born to the year I was born.
## Ryan
I created code which solved each of the four data science problems in the lab report. I created metrics which I thought best answered each question, and then created plots to best display the data as the answers.




## Chris

                                                                        