---
title: "Untitled"
author: "Chris"
date: "2018/4/11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

library(gapminder)
```

# Analyzing life expectancy vary and GDP per capita by decades

# Team Work
### How does life expectancy vary by continent and by decade? 
```{r}

```



### How does GDP per capita vary by continent and by decade? 
```{r}

```


 
# Summary of Who did What

## Lauren


## Kaite


## Ryan


## Chris
I tried to analysis the 5 decades the life expectancy and the gdp per capita, first time I just used subset to five indiviual continent and use the aggregate function tried to calculate the answer, but the only things that i can find is the averge answer durning the whole time and I stuck in every decades, so I used another way tried to find the relation durning the plots. for each question I created 5*5 plots. 5 contients and 5 decedes, and from the graphs that I got, it is really easy to conclude that the life expectancy and the cgp per capita increase when the years increase.


# Individual Work

## Lauren
### How does life expectancy vary by continent and by decade? 
```{r}

```

### How does GDP per capita vary by continent and by decade? 
```{r}

```



## Kaite
### How does life expectancy vary by continent and by decade? 
```{r}

```



### How does GDP per capita vary by continent and by decade? 

```{r}

```


## Ryan
### How does life expectancy vary by continent and by decade? 
```{r}

```


### How does GDP per capita vary by continent and by decade? 
```{r}

```



## Chris
### How does life expectancy vary by continent and by decade?

```{r}
Europe <- subset(gapminder, continent == "Europe")
Africa <- subset(gapminder, continent == "Africa")
Asia <- subset(gapminder, continent == "Asia")
Americas <- subset(gapminder, continent == "Americas")
Oceania <- subset(gapminder, continent == "Oceania")
aggregate(lifeExp~continent, gapminder, min)
aggregate(lifeExp~continent, gapminder, max)
aggregate(lifeExp~continent, gapminder, mean)
aggregate(lifeExp~continent, gapminder, median)
aggregate(lifeExp~continent, gapminder, IQR)


```


```{r}
filter(gapminder,(continent=="Europe" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Europe" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Europe" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

filter(gapminder,(continent=="Europe" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Europe" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

```

```{r}
filter(gapminder,(continent=="Africa" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Africa" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Africa" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

filter(gapminder,(continent=="Africa" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Africa" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

```


```{r}
filter(gapminder,(continent=="Asia" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Asia" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Asia" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

filter(gapminder,(continent=="Asia" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Asia" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
```

```{r}
filter(gapminder,(continent=="Americas" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Americas" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Americas" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

filter(gapminder,(continent=="Americas" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Americas" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

```

```{r}
filter(gapminder,(continent=="Oceania" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

filter(gapminder,(continent=="Oceania" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=lifeExp),binwidth=1)

```


### How does GDP per capita vary by continent and by decade? 

```{r}
europe <- subset(gapminder, continent == "Europe")
africa <- subset(gapminder, continent == "Africa")
asia <- subset(gapminder, continent == "Asia")
americas <- subset(gapminder, continent == "Americas")
oceania <- subset(gapminder, continent == "Oceania")
aggregate(gdpPercap~continent, gapminder, min)
aggregate(gdpPercap~continent, gapminder, max)
aggregate(gdpPercap~continent, gapminder, mean)
aggregate(gdpPercap~continent, gapminder, median)
aggregate(gdpPercap~continent, gapminder, IQR)
```

```{r}
filter(gapminder,(continent=="Europe" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Europe" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Europe" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Europe" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Europe" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
```

```{r}
filter(gapminder,(continent=="Africa" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Africa" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Africa" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Africa" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Africa" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
```

```{r}
filter(gapminder,(continent=="Asia" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Asia" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Asia" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Asia" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Asia" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
```

```{r}
filter(gapminder,(continent=="Americas" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Americas" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Americas" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Americas" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Americas" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
```


```{r}
filter(gapminder,(continent=="Oceania" & year<1970 & year >= 1960)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<1980 & year >= 1970)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<1990 & year >= 1980)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<2000 & year >= 1990)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
filter(gapminder,(continent=="Oceania" & year<2010 & year >= 2000)) %>%
  ggplot() +
  geom_freqpoly(aes(x=gdpPercap),binwidth=1)
```



