
---
title: "Lab3"
author: "Lauren Gregg, Katie Jiang, Ryan Marizza, Chris He"
date: "1/31/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```

# Team Work

## Overall Question:
How is general health related to weight and exercise?

It is commonly thought an individual in good health exercises frequently and has a lower weight. However, this is not always the case. It is important to compare general health with weight and exercise in order to determine if there is a correlation between the two and if any outliers exist.

## Plot to answer the Question

## Conclusion

## Recommendation for Action


# Individual Work

## Lauren
```{r}
ggplot(data = cdc, mapping = aes(y=weight, x=wtdesire)) +
  geom_point() +
  facet_wrap(~exerany) + 
  geom_jitter() + 
  coord_fixed() +
  geom_smooth(aes(color=gender), method = "lm") +
  geom_abline()
```

The data has been divided into two groups: 1 indicates that the individuals have exercised in the past month and 0 indicates otherwise. Additionally, a linear fit has been assigned to males (m) and females (f) comparing individuals actual weight versus desired weight. I have also included a black line; this line indicates an individual whose desired weight is his actual weight.

With this understanding of the plot, we can make some interesting observations. In both the exercise and non-exercise groups, the linear fit for males is closest to the control line. 

## Kaite

## Ryan

## Chris


# Summary of Who did What

## Lauren


## Kaite

## Ryan

## Chris



# Individual Work


