
---
title: "Lab3"
author: "Lauren Gregg, Katie Jiang, Ryan Marizza, Chris He"
date: "1/31/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
install.packages("tidyverse")
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```

# Team Work

## Overall Question:
How is general health related to weight and exercise?

It is commonly thought an individual in good health exercises frequently and has a lower weight. However, this is not always the case. It is important to compare general health with weight and exercise in order to determine if there is a correlation between the two and if any outliers exist.

## Plot to answer the Question

## Conclusion

## Recommendation for Action

# Individual Work

## Lauren

## Kaite
```{r}
library(tidyverse)
install.packages("tidyverse")
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
ggplot(data = cdc,mapping = aes(x = weight, y = exerany, color = gender))+
  geom_smooth(method = "lm")+
  facet_wrap(~genhlth)+
  labs(x = "weight",y = "exerany",title="The linear relationship between weight, gender and exerany")

```


## Ryan

## Chris


# Summary of Who did What

## Lauren


## Kaite
  Due to that our main question is about exercise and the I plot the relationship between weight, gender and exerany
## Ryan

## Chris





