---
title: "Lab 4: Smoking and Low Birth Weight"
author: "10th-statistics-division"
date: "2/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`) #renaming `bwt/oz` because the "/" sign requires special care
```

# Motivating Questions
1. Does Smoking Lead to Babies Born Prematurely?
2. Does Smoking lead to Babies with Low Birth Weight?

##Preliminary Question
1. Which Variables are Similar between Smokers and Nonsmokers? Which are different?

-- We definitely dont need to show ALL of these plots, I was just playing around and couldnt find a significant difference in any variables between smokers and nonsmokers

```{r, prelim_question_parity}
#Which Variables are Similar between Smokers and Nonsmokers? Which are different?
#   the main questions are about premature and birth weight already

ggplot(data=babies, mapping = aes(parity)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_MothersRace}
ggplot(data=babies, mapping = aes(mrace)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_FathersRace}
ggplot(data=babies, mapping = aes(drace)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_FathersRace}
ggplot(data=babies, mapping = aes(drace)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_MomsAge}
ggplot(data=babies, mapping = aes(mage)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_MomsEducation}
ggplot(data=babies, mapping = aes(x=as.character(smoke), y=med)) +
  geom_boxplot() 

```

```{r, prelim_question_gestation}
ggplot(data=babies, mapping = aes(x=as.character(smoke), y=gestation)) +
  geom_boxplot() 

```


## Importance of the Questions:

  Generally speaking, smoking is harm for our body. But in society, a lot of people still smoke and the tendency for women smoking is increasing, which may have some negative effect on next generation. Babies are significant in a family, and also important for our future, thus in order to figure out what kind of effect of smoking will lead to on both mother and babies, we analyzed whether smoking Lead to Babies Born Prematurely and whether smoking lead to Babies with Low Birth Weight. These results will give us solid solutions to smoking effects on babies and mothers. 

## Conclusions
1. Does smoking lead to babies being born prematurely?

```{r, Q1}
ggplot(data=babies, mapping=aes(Premature, color=Premature)) + 
  geom_bar() +
  facet_wrap(~babies$smoke)
```

```{r, Q1cont}
NonSmokePrem <- length(which(babies$Premature==1 & babies$smoke==0))
SmokePrem <- length(which(babies$Premature==1 & babies$smoke==1))

NonSmokers <- length(which(babies$smoke==0))
Smokers <- length(which(babies$smoke==1))

RatioNonSm <- NonSmokePrem/NonSmokers
RatioSm <- SmokePrem/Smokers
```
```{r}
RatioNonSm
```
```{r}
RatioSm
```
In the sample, the group of mothers who smoke, did have a greater percentage of premature births. However, I am unsure if the difference in these values are statistically significant.
** Note: i want to ask Prof. about significance testing - ANOVA or t-test


2. Does Smoking lead to Babies with Low Birth Weight?

```{r, Q2}
ggplot(data=babies, mapping=aes(y=bwtoz, x=smoke, color=as.factor(smoke))) +
  geom_boxplot()
```

Again, it appears that the mothers who smoke give birth to children with, on average, a lower birth rate than mothers who do not smoke. I do not know if this difference is statistically significant. 

# Recommendation


# Individual Findings

## Lauren 
My Question:
  It may seem intuitive that the longer a baby is in the womb, the bigger that baby will be! Is the length of gestation related to a baby's birthweight? What other factors may contribute to a baby's birthweight?

```{r, gestation_v_birthweight}
ggplot(data=babies, mapping=aes(x=gestation, y=bwtoz))+
  geom_point()+
  geom_jitter() +
  geom_smooth(method="lm") +
  geom_smooth(method = "loess", color="green")
```
```{r, gestation_v_birthweightCorrelation}
#cor(na.omit(babies$gestation), na.omit(babies$bwtoz))
###NEED TO ASK PROFESSOR###
```


There appears to be some linear relationship between gestation and birthweight.This was too be expected. 

```{r, gestation_v_birthweight-NoPrem}
#babies[as.character(babies$Premature)!=1]
df = babies[ !grepl("1", babies$Premature) , ] #getting rid of premature data

ggplot(data=df, mapping=aes(x=gestation, y=bwtoz))+
  geom_point()+
    geom_jitter()+
  geom_smooth(method="lm") +
  geom_smooth(method = "loess", color="green")
```

Babies who are born prematurely tend to be underweight. When focus on babies who had reach full term, we see a linear relationship between gestation and birthweight still exists, but it is less dramatic. 

This relationship seems pretty obvious, but other factors may play a role in a babies birthweight. Below we look at the mother's weight and the father's weight in comparison to the child's birthweight.

```{r, brtweight_v_momWeight}
ggplot(data=babies, mapping=aes(x=babies$bwtoz,y=babies$mpregwt)) + 
  geom_point() + 
  geom_jitter() +
  geom_smooth() + 
  geom_smooth(method="lm", color="green")
```

```{r, brtwght_v_dadWright}
ggplot(babies, aes(x=bwtoz, y=dwt)) +
  geom_point() + 
  geom_jitter() +
  geom_smooth() + 
  geom_smooth(method="lm", color="green")

```



## Katie
My question:
 Does Smoking make short gestation days and premature birth, which causes light baby weight?
```{r}
ggplot(data = babies,mapping = aes(x = gestation  , y = bwtoz,color = Premature ))+
  facet_wrap(~smoke)+
  geom_smooth(method = "loess")+
  geom_jitter()+
  labs(x="gestation (days)",y = "baby birth weight (ounces)",title = "Gestation days and premature birth compares babies weight,\n whether mothers smoke")
```
```{r}
ggplot(data = babies,mapping = aes(x = gestation  , y = bwtoz,color = Premature))+
  geom_col()+
  facet_wrap(~smoke)+
  labs(x="gestation (days)",y = "baby birth weight (ounces)")
```
#Explanation
Based on my question which is Does Smoking make short gestation days and premature birth, which causes light baby weight? I use aesthetic function to set x equals gestation days, y equals babies weight and make the color to represent premature scale. After the basic elements of this graph, I added geom_smooth setting method equals ??loess?? and geom_jitter, which gives us a curve and more random points representing the relationship between gestation days and babies?? weight. Then I use facet_wrapp to divide the plot into three parts: smoking, nonsmoking and don??t know. In order to compare the number of mothers having gestation days and premature births, I plot another geom_col graph. In this case, we can visualize from the graph that whether mothers smoke or not, there are around 1/3 of them have premature births, but the number of smoking mothers having premature births is more than those nonsmoking. And those babies of nonsmoking mothers are heavier than smoking ones. 

Therefore, my answer is yes. Smoking makes premature birth which cause light weight of babies. 
## Chris

## Ryan

##Contributions
## Lauren 

## Katie

## Chris

## Ryan