---
title: "Lab 4: Smoking and Low Birth Weight"
author: "10th-statistics-division"
date: "2/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`) #renaming `bwt/oz` because the "/" sign requires special care

##PROFESSOR?? can I preprocess the data and just delete all of the NA rows
babies1 <- na.omit(babies)
```

# Motivating Questions
1. Does Smoking Lead to Babies Born Prematurely?
2. Does Smoking lead to Babies with Low Birth Weight?

##Preliminary Question
1. Which Variables are Similar between Smokers and Nonsmokers? Which are different?

-- We definitely dont need to show ALL of these plots, I was just playing around and couldnt find a significant difference in any variables between smokers and nonsmokers

```{r, prelim_question_parity}
#Which Variables are Similar between Smokers and Nonsmokers? Which are different?
#   the main questions are about premature and birth weight already

ggplot(data=babies, mapping = aes(parity)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_MothersRace}
ggplot(data=babies, mapping = aes(mrace)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_FathersRace}
ggplot(data=babies, mapping = aes(drace)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_FathersRace}
ggplot(data=babies, mapping = aes(drace)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_MomsAge}
ggplot(data=babies, mapping = aes(mage)) +
  geom_bar() +
  facet_wrap(~smoke)

```

```{r, prelim_question_MomsEducation}
ggplot(data=babies, mapping = aes(x=as.character(smoke), y=med)) +
  geom_boxplot() 

```

```{r, prelim_question_gestation}
ggplot(data=babies, mapping = aes(x=as.character(smoke), y=gestation)) +
  geom_boxplot() 

```


## Importance of the Questions:

  Generally speaking, smoking is harm for our body. But in society, a lot of people still smoke and the tendency for women smoking is increasing, which may have some negative effect on next generation. Babies are significant in a family, and also important for our future, thus in order to figure out what kind of effect of smoking will lead to on both mother and babies, we analyzed whether smoking Lead to Babies Born Prematurely and whether smoking lead to Babies with Low Birth Weight. These results will give us solid solutions to smoking effects on babies and mothers. 

## Conclusions
1. Does smoking lead to babies being born prematurely?

```{r, Q1}
ggplot(data=babies, mapping=aes(Premature, color=Premature)) + 
  geom_bar() +
  facet_wrap(~babies$smoke)
```

```{r, Q1cont}
NonSmokePrem <- length(which(babies$Premature==1 & babies$smoke==0))
SmokePrem <- length(which(babies$Premature==1 & babies$smoke==1))

NonSmokers <- length(which(babies$smoke==0))
Smokers <- length(which(babies$smoke==1))

RatioNonSm <- NonSmokePrem/NonSmokers
RatioSm <- SmokePrem/Smokers
```
```{r}
RatioNonSm
```
```{r}
RatioSm
```
In the sample, the group of mothers who smoke, did have a greater percentage of premature births. However, I am unsure if the difference in these values are statistically significant.
** Note: i want to ask Prof. about significance testing - ANOVA or t-test


2. Does Smoking lead to Babies with Low Birth Weight?

```{r, Q2}
ggplot(data=babies, mapping=aes(y=bwtoz, x=smoke, color=as.factor(smoke))) +
  geom_boxplot()
```

Again, it appears that the mothers who smoke give birth to children with, on average, a lower birth rate than mothers who do not smoke. I do not know if this difference is statistically significant. 

# Recommendation


# Individual Findings

## Lauren 
My Question:
  It may seem intuitive that the longer a baby is in the womb, the bigger that baby will be! Is the length of gestation related to a baby's birthweight? What other factors may contribute to a baby's birthweight?
  When my sister was pregnant, she was so concerned about going past her due date, joking that she did not want the baby to be any bigger than she needed to be. This is what influences my question. I hope to have data to show my sister that their is or is not fact behind her humor. 

```{r, gestation_v_birthweight}
ggplot(data=babies, mapping=aes(x=gestation, y=bwtoz))+
  geom_point()+
  geom_jitter() +
  geom_smooth(method="lm") +
  geom_smooth(method = "loess", color="green")
```
```{r, gestation_v_birthweightCorrelation}
#cor(na.omit(babies$gestation), na.omit(babies$bwtoz))
cor(babies1$gestation, babies1$bwtoz)
```


There appears to be some linear relationship between gestation and birthweight.This was too be expected. 

```{r, gestation_v_birthweight-NoPrem}
#babies[as.character(babies$Premature)!=1]
df = babies[ !grepl("1", babies$Premature) , ] #getting rid of premature data

ggplot(data=df, mapping=aes(x=gestation, y=bwtoz))+
  geom_point()+
    geom_jitter()+
  geom_smooth(method="lm") +
  geom_smooth(method = "loess", color="green")
```

```{r, gestation_v_birthweightCorrelation}
df1 = na.omit(df)
cor(df1$gestation, df1$bwtoz)
```

Birthweight and length of gestation are clearly related with a correlation coeffecient of 0.392. However, babies who are born prematurely tend to be outliers - as seen in the firts plot. When we focus on babies who had reach full term, we see a linear relationship between gestation and birthweight still exists, but it is less dramatic. In fact, when we consider a curved best fit (the green line), rather than a linear best fit (the blue line), we see a decline in birth weight beginning around day 290. This fit still has a pretty large standard error, shown by the gray color surrounding the green line. The correlation coefficient between birthweight and length of gestation for babies who reached full term is 0.178. 

Ultimately, the relationship between birthweight and gestation period is pretty obvious, but other factors may play a role in a babies birthweight. Below we look at the mother's weight and the father's weight in comparison to the child's birthweight.

```{r, brtweight_v_momWeight}
ggplot(data=babies, mapping=aes(x=babies$bwtoz,y=babies$mpregwt)) + 
  geom_point() + 
  geom_jitter() +
  geom_smooth() + 
  geom_smooth(method="lm", color="green")
```

```{r, brtwght_v_dadWright}
ggplot(babies, aes(x=bwtoz, y=dwt)) +
  geom_point() + 
  geom_jitter() +
  geom_smooth() + 
  geom_smooth(method="lm", color="green")

```


```{r, mpregwt_v_bwtoz_corr}
cor(babies1$mpregwt,babies1$bwtoz)
```


```{r, dwt_v_bwtoz_corr}
cor(babies1$dwt, babies1$bwtoz)
```

Based on the plots and the correlation coefficients, there is an extrememly weak correlation between the parents' weight and the baby's birthweight. In fact, this relationship is so weak that I am able to say the birthweight is not impacted by the parents weight. 

To completely answer my initial question, there is a moderate correlation between length of gestation and a baby's birthweight when I consider children born premature. However, when I consider only babies who have reached full term, the correlation coefficient changes and tells us that a baby's weight is not correlated to the gestation period after 270 days. When I attempted to identify other influencing factors of birthweight, I considered the mother's and father's weight. Again, the correlation coefficient were not large enough to conclude a relationship exists. 

To continue answering this question, I could compare a baby's birthweight to other variables within our dataframe - mother's height, father's height, mother's race, or number of cigarettes smoked a day. I believe that gestation period will remain the most influencing factor of a bay's birthweight, even though the relationship does not appear to be very strong.


## Katie
My question:
 Does Smoking make short gestation days and premature birth, which causes light baby weight?
```{r}
ggplot(data = babies,mapping = aes(x = gestation  , y = bwtoz,color = Premature ))+
  facet_wrap(~smoke)+
  geom_smooth(method = "loess")+
  geom_jitter()+
  labs(x="gestation (days)",y = "baby birth weight (ounces)",title = "Gestation days and premature birth compares babies weight,\n whether mothers smoke")
```
```{r}
ggplot(data = babies,mapping = aes(x = gestation  , y = bwtoz,color = Premature))+
  geom_col()+
  facet_wrap(~smoke)+
  labs(x="gestation (days)",y = "baby birth weight (ounces)")
```
#Explanation
Based on my question which is Does Smoking make short gestation days and premature birth, which causes light baby weight? I use aesthetic function to set x equals gestation days, y equals babies weight and make the color to represent premature scale. After the basic elements of this graph, I added geom_smooth setting method equals ??loess?? and geom_jitter, which gives us a curve and more random points representing the relationship between gestation days and babies?? weight. Then I use facet_wrapp to divide the plot into three parts: smoking, nonsmoking and don??t know. In order to compare the number of mothers having gestation days and premature births, I plot another geom_col graph. In this case, we can visualize from the graph that whether mothers smoke or not, there are around 1/3 of them have premature births, but the number of smoking mothers having premature births is more than those nonsmoking. And those babies of nonsmoking mothers are heavier than smoking ones. 

Therefore, my answer is yes. Smoking makes premature birth which cause light weight of babies. 
## Chris

## Ryan

##Contributions
## Lauren 

## Katie

## Chris

## Ryan