---
title: "Lab5"
author: "Lauren, Chris, Ryan, Katie"
date: "2/16/2018"
output: html_document
---

```{r setup, include=FALSE}
## notice i load the data here so we dont have to do it each indiviudally
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
ms <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/ms.csv") # load the data
```

# Team 

```{r}
ggplot(ms, aes(spec5)) +
  geom_histogram()
```

This is a simple plot of the raw spec5 data. We see that there are so many values at or near 0 that we are unable to see any information at other values.

```{r}

ms_4 <- ms %>% filter(spec5 > 1 & spec5<10000)%>%mutate(log.spec5 = log10(spec5),log.spec10 =log10(spec10),diff = abs(spec5-spec10)) #create the new dataset

ggplot(data = ms_4,aes(x=mass,y = log.spec5))+geom_violin() #the plot of mass vs. log spec5

```

This is a log transform of the spec5 data compared against the mass. 


```{r}

ms5 <- ms_4 %>% filter(diff<150)
ggplot(data = ms5,aes(x=diff))+geom_histogram()
```

This shows the difference between the two variables, sepc5 and spec10. We considered only values less then 150 in order to see a distribution pattern.



# Lauren Gregg
## Variance
```{r}
msLG <- ms %>% filter(mass>50)
ggplot(data=msLG, aes(mass, spec5)) + 
  geom_point()
```

Because so many values of mass are close to zero, it is difficult to see the variance in the "heavier" particles. I decided to filter all particles with mass less than 50 out of the data set. Plotting this data, we can see peaks occur around masses of 75, 150, 175, 210, 275, and 350. This is not visible without filtering the data.

## Covariance
```{r}
ggplot(data=msLG, aes(spec5, spec10)) +
  geom_point()
```

In order to continue on my path, I was interested in seeing if a strong correlation between spec5 and spec10 was still visible when considering only the objects with mass greater than 50. The covariation between the variables is still very evident. 

```{r}
cor(msLG$spec5, msLG$spec10)
```

```{r}
cor(ms$spec10, ms$spec5)
```

The correlation is moderate with a coeffecient of 0.67. However, this is much less than the coefficient of 0.99, which is the result if we consider objects with a mass less than 50.

#Katie

##Variance
```{r}
#install.packages("hexbin")
library(hexbin)
ms %>% summarise(total = length(spec5),
                 numNAs = sum(is.na(spec5)),
                 neg = length(spec5[spec5<0]), 
                 zero = length(spec5[spec5==0]),
                 small = length(spec5[spec5>0 & spec5<=100]),
                 med = length(spec5[spec5>100 & spec5<=1000]),
                 large = length(spec5[spec5>1000 & spec5<=10000]),
                 realbig = length(spec5[spec5>10000 & spec5<=100000]))

mas<-ms %>% filter(spec10>0 & spec10 <5000 & mass < 200) %>% mutate(log(spec10)) %>% arrange(desc(spec10))
ggplot(mas)+
  geom_hex(mapping = aes(y = spec10, x = mass))
```

First I plot the variation about the spec10 with mass without filtering, and I found there are lots of points stick together and the density is large, and it's hard to visualize the actual spec10 points. So I narrowed down the scales , took the logarithm and pick some specific arranges about the data, in this case, it's easier to read the tendency and the spread of those points.

## Covariance
```{r}
#install.packages("GGally")
library(GGally)
mms <- ms %>% filter(spec5>0 & spec5<5000 & spec10>0 & spec10<5000) 
mea <- mms %>% summarise(mean(spec5),mean(spec10))
mea
ggplot(mms,mapping = aes(y = spec5,x = spec10,color = mass))+
  geom_point()+
  geom_smooth(method = "lm", se = TRUE)+
  labs(x = "spec10",y = "spec5",title = "The corelation between spec5 and spec10, and their mean values are \n spec5:30.23052, spec10: 26.9792")
```
For the correlation part, I narrowed it down and pick the same scale to plot the points for each variable. Then I calculated the mean value for spec5 and spec10, which I found they??re close. The mean for spec5 is 30.23052, for spec10 is 26.9792, and the close relationship could be visualize from the plot---they are not far away from each other. 

#Ryan
##Variance of Spec5
```{r}

#one individual plot

ggplot(data = ms_4,aes(x=mass,y = log.spec5))+geom_bin2d(binwidth = c(5,0.1))
```

In classic mass spectrometry form, this plot shows spikes of the spec5 variable for certain mass/charge ratios. Since the spikes give some information about the composition of the material, I thought it best to create a plot which excentuates these spikes. Unfortunatley, the spikes for masses between 0 and 50 are immense, so the normal histogram does a poor job at displaying the spec5 spikes at higher mass/charge ratios. My solution was to display log(spec5) vs. mass. The count (displayed with a color gradient) is useful to visualize where the majority of the data was collected. From this, one can easily see that a large majority of the data was collected in the low mass/charge reigon. 

##Covariance of Spec5 and Spec10
```{r}

#the other individual plot
ggplot(data = ms_4,aes(x=spec5,y =spec10))+geom_point()

```

I've chosen to display the covariation of the spec10 and spec5 variables using a dot plot. The dot plot does the job well because of the extremely strong correlation between spec5 and spec10. The most astounding thing about this plot, is that there seems to be a bilinear (I made that word up, but it seems nice) relationship between spec5 and spec10, in which points fall either on a line with a high slope(the top points), or on a line with a low slope (the bottom points). 










