---
title: "Lab_15"
author: "Lauren, Katie, Ryan,Chris"
date: "5/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(stringr)
options(na.action = na.warn)
summaryhealth <- read.csv("Summaryhealth.csv")
```

# Overall Question

## Description of the dataset

## Why it is interesting/important

## What new tools that we applied?


# Conclusion

# Recommendation

# Individual Findings

## Lauren 
### Subquestion

#### why it is important?


## Katie
### Subquestion
How does the average life expectancy relate with unhealthy days for each state? And which western state has the highest slope? Is that a coincident?
#### why it is important?
Because one of the important element related to the life expectancy is unhealthy factors, so I want to explore the their relationship by creating models. And we are in Colorado which belongs western states in the US, so in the life expectancy model, I want to see which western state has the highest slope and compare it with mixed state random samples to see whether it is real highest.

#### New tool I used
I used many models and some map functions, which could apply the model to each state and generate the pattern. Also I implemented the new idea which is mixed label and then plot the distribution of the spread data. 

```{r}
summaryhealth[summaryhealth == -1111.1]<- NA
summaryhealth <- na.omit(summaryhealth)
data <- summaryhealth %>% select(c(CHSI_County_Name,CHSI_State_Name, CHSI_State_Abbr,ALE,All_Death,Health_Status,Unhealthy_Days))

```
I created the country model for each state and plot the residuals for each model in each state.
We can see the boxplot below, nearly all the state are around the 0 residuals and some of the states have the large range of life expectancy with unhealthy days. But the tendency is decreasing as the life expectancy increases.
```{r}
country_model <- function(df){
  lm(ALE ~ Unhealthy_Days,data = df)
}
models <- map(data1$data, country_model)
dataWithModels <- data1 %>% mutate(models)
dataWithModels <- dataWithModels %>% mutate(resid = map2(data,models,add_residuals))

resids <- unnest(dataWithModels,resid)

resids %>%
  ggplot(aes(CHSI_State_Abbr,resid))+
  geom_boxplot()+
  ggtitle("Residuals vs. State")

```
I first filter the state names for western states, and took the descing of the data to find the max slope which lies in Wyoming. Then  I mixed the state and randomly chose 13 states to see the maximum and compared it with wyoming.

```{r}
get_slope <- function(model){
  model$coefficients[[2]]
}
western <- dataWithSlope %>% filter(str_detect(CHSI_State_Name,"Montana|Colorado|Wyoming|New Mexico|Idaho|Utah|Arizona|Nevada|Washington|Oregon|California|Alaska|Hawaii"))
western %>% arrange(desc(slopes))#Wyoming 
#-0.0195119
slopes <- map_dbl(dataWithModels$models, get_slope)

dataWithSlope <- dataWithModels %>% mutate(slopes)


mixedcountry <- vector("double",length = 13)
for (i in seq_along(mixedcountry)) {
  temp <- sample(dataWithSlope$slopes,1)
  if(is.na(temp)){
    temp <- sample(dataWithSlope$slopes,1)
  }
  mixedcountry[i] <- temp
}
ggplot()+
  geom_histogram(aes(x = mixedcountry),bins = 20)
max(mixedcountry)
```
We can see after ploting several distributions,if the max of mixedcountry is less than -0.0195119, the Wyoming is actually high slope based on all the states, and that is not coinsidence.
## Ryan
### Subquestion


## Chris
### Subquestion

# Team goal reflections

# Individual Reflections on goals
## Lauren

## katie
Personally, I think I would not change my 6 month-goal after graduation as well as the 2-year-goal. Because I am still following my plan like that, and I feel that is what I want to do in future. But maybe I will modify some details about my goals as I go through the university. So I wouldn¡¯t change it so far.

For the initial goals and hopes, I would say although I might not really achieve the master level of R coding, but at least I learned how to implement code in R to analyze a big data, I knew how to build a model based on the relationship of data, and I formed an idea to deal with untidy data. In my perspective, I reached my goals for this course, but I don¡¯t satisfy. Because I think I still need more practice to manipulate with other different types of data. 

If I could give myself advice at the beginning of this course, I would say when you are doing readings and find something confusing, try to find some online tutorials for r and watch the videos, which helps a lot!  
## Chris

## Ryan


# Contributions
### Lauren 


### Katie
I outlined the lab 15, and gave some suggestions about our data-set. Then I went through what we learned recently and found related sub-questions corresponding to our data set. I first created a state model which forms a linear relationship between average life expectancy and unhealthy days, and then applied it to each state. After getting the model for each state, I am interested in western states in the US(Because we are in western states), So I found the max slope of the western state by using str_detect, and then I mixed the states and randomly pick same number to see whether the highest slope in western state is coincidence.
### Chris


### Ryan